SPARQL on the Open, Decentralised Web

### 2016-07-23 dissertation/papersincontext.tex
Small

This direction was motivated by a dissatisfaction with the methodology
used in the literature, specifically benchmarking, to test assertions
of performance. That lead to exploration of statistical methods referenced
in Section~\ref{sec:condoe}, and to the organising of the Empirical 2014
Workshop at the Extended Semantic Web Conference (which I was
unfortunately prevented from attending myself). Still, frustrated by
the slow progress of the last 16 years, and the difficulty in comparing
methods to the more mature natural sciences, I still felt the need to
express a philosophical view of science, which I did by submitting an
article to the ``Negative or inconclusive results in Semantic Web''
workshop at the Extended Semantic Web Conference 2015. The essay, see
\cite{kjernsmo_noise_2015} was tangential to the Call for Papers, but
the chairs decided to accept it as an interview. With Ruben Verborgh
in the role of the interviewer, we reformulated it as
\cite{kjernsmo_noise_2015_interview}, which was published in the
proceedings and is included in the dissertation. It was performed with
Jacco van Ossenbruggen as the interviewer in front of the
audience. The essay, at
\url{http://folk.uio.no/kjekje/2015/noise-essay.html} is however a
more thorough account.

>>>>

This direction was motivated by a dissatisfaction with the methodology
used in the literature, specifically benchmarking, to test assertions
of performance. That lead to exploration of statistical methods referenced
in Section~\ref{sec:condoe}, and to the organising of the Empirical 2014
Workshop at the Extended Semantic Web Conference (which I was
unfortunately prevented from attending myself). Frustrated by
the slow progress of the last 16 years, and the difficulty in comparing
methods to the more mature natural sciences, I still felt the need to
express a philosophical view of science, which I did by submitting an
article to the ``Negative or inconclusive results in Semantic Web''
workshop at the Extended Semantic Web Conference 2015. The essay, see
\cite{kjernsmo_noise_2015} was tangential to the Call for Papers, but
the chairs decided to accept it as an interview. With Ruben Verborgh
in the role of the interviewer, we reformulated it as
\cite{kjernsmo_noise_2015_interview}, which was published in the
proceedings and is included in the dissertation. It was performed with
Jacco van Ossenbruggen as the interviewer in front of the
audience. The essay, at
\url{http://folk.uio.no/kjekje/2015/noise-essay.html} is however a
more thorough account.
